A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-15 doc/draft-01-stokes/04numerical.tex
updating makefile, adding acks, adding affils, and cleaning figs
add info on software location and cpu used
update url
add note about order of ggq

In this section, we demonstrate the analytical
claims above with numerical examples and
highlight the performance of the BIE approach
with demonstrations on domains of analytical
and practical interest.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{media/annulus_discretization.pdf}
\caption{Sample discretization of an annulus, where the inner
circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
is discretized using $10$ panels.}
\label{fig:panels}
\end{figure}
%
Another important quantity below is the
arc-length density of a panel, which
we denote by $s_j(t) := |\bx'_j(t)|$.
%
Finally, we denote the set of panels
which are adjacent to panel $j$
by $A(j)$. On a closed curve,
$A(j)$ contains two integers.

@@

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the rules we used, $N_s = 16$ and
$N_a = 48$.
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

@@

\begin{remark}
  \label{rmk:levelrestrict}
  We ensure that ``far'' interactions
  are handled to high precision by requiring that
  no two adjacent panels differ in length
  by more than a factor of 2. On a domain which does
  not nearly self-intersect this
  guarantees that no ``far'' interactions occur
  which are much closer than 1/2 of a panel away
  (assuming panels are relatively flat).
  Because the location of the singularity is
  bounded away from the panel and the smooth
  rule is of high order, we obtain a quadrature
  rule with sufficient precision.
\end{remark}

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Note that $N^{-20}$ is the expected order of
convergence for Generalized Gaussian quadrature for weakly 
singular integrals.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

\begin{figure}
  \centering
  \includegraphics[width=0.98\textwidth]{media/conv-studies.pdf}
  \caption{Convergence studies for the Dirichlet eigenvalues
  computed using the integral equations 
  $\cI - 2\cD_{k} - 2\cW$ (left) and
  $\cI - 2\cD_{k} - 2i \cS_{k} - 2\cW$ (right).}
  \label{fig:conv}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.98\linewidth]{media/det_spur.pdf}
\caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 
and $f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}|=6.8\times 10^{-12}$.
On the other hand $|f_{C}^{N}(k_{0})|=0.42$, and thus $\cI-2\cD_{k}-2i\cS_{k} 
-2\cW$ has no 
spurious eigenvalue in the neighborhood of $k=k_{0}$.}
\label{fig:spur}
\end{figure}

\subsubsection{Speed}
\label{subsec:speed}
In this section, we demonstrate the $O(N\log{N})$ scaling of evaluating
$f^{N}_{C}(k)$ as long as $N$ is large enough to resolve the interactions
at the Helmholtz parameter $k$. 
When $N$ is smaller than that, we observe a worse scaling since the
assumption that far-interactions are low-rank is no longer valid at
the tolerance of FLAM.
We plot the timing results corresponding to three different values of 
$k$ in~\cref{fig:speed}.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{media/speed_res.pdf}
\caption{Time taken $(t)$ in seconds to evaluate the determinant $f_{C}^{N}(k)$ as
a function of $N$ for three different values of $k$.}
\label{fig:speed}
\end{figure}

>>>>

In this section, we demonstrate the analytical
claims above with numerical examples and
highlight the performance of the BIE approach
with demonstrations on domains of analytical
and practical interest. The software used to
generate the figures is available online
\footnote{\texttt{https://doi.org/10.5281/zenodo.2641296}}.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{fig/annulus_discretization.pdf}
\caption{Sample discretization of an annulus, where the inner
circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
is discretized using $10$ panels.}
\label{fig:panels}
\end{figure}
%
Another important quantity below is the
arc-length density of a panel, which
we denote by $s_j(t) := |\bx'_j(t)|$.
%
Finally, we denote the set of panels
which are adjacent to panel $j$
by $A(j)$. On a closed curve,
$A(j)$ contains two integers.

@@

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the 20th-order rule we used, $N_s = 16$ and
$N_a = 48$. 
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

@@

\begin{remark}
  \label{rmk:levelrestrict}
  We ensure that ``far'' interactions
  are handled to high precision by requiring that
  no two adjacent panels differ in length
  by more than a factor of 2. On a domain which does
  not nearly self-intersect this
  guarantees that no ``far'' interactions occur
  which are much closer than 1/2 of a panel away
  (assuming panels are relatively flat).
  Because the location of the singularity is
  bounded away from the panel and the smooth
  rule is of high order, we obtain a quadrature
  rule with sufficient precision.

  The overall order of accuracy of the GGQ we use
  is 20th-order, up to the precision of the ``far''
  interactions.
\end{remark}

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Recall that the GGQ we use has an expected order
of convergence of $N^{-20}$ for evaluating convolutions
with such integral kernels,
so that the error of the roots is observed to have the
same order as the quadrature rule.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

\begin{figure}
  \centering
  \includegraphics[width=0.98\textwidth]{fig/conv-studies.pdf}
  \caption{Convergence studies for the Dirichlet eigenvalues
  computed using the integral equations 
  $\cI - 2\cD_{k} - 2\cW$ (left) and
  $\cI - 2\cD_{k} - 2i \cS_{k} - 2\cW$ (right).}
  \label{fig:conv}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.98\linewidth]{fig/det_spur.pdf}
\caption{The values of the discretized determinants $f_{C}^{N}(k)$ (left)
and $f_{D}^{N}(k)$ on the interval $k=[13,14]$ with $N=368$. The vertical
dotted line denotes the spurious eigenvalue $k_{0} = 14.79595178235126$ 
and $f_{D}^{N}(k_{D}) = 0$ with $|k_{D}-k_{0}|=6.8\times 10^{-12}$.
On the other hand $|f_{C}^{N}(k_{0})|=0.42$, and thus $\cI-2\cD_{k}-2i\cS_{k} 
-2\cW$ has no 
spurious eigenvalue in the neighborhood of $k=k_{0}$.}
\label{fig:spur}
\end{figure}

\subsubsection{Speed}
\label{subsec:speed}
In this section, we demonstrate the $O(N\log{N})$ scaling of evaluating
$f^{N}_{C}(k)$ as long as $N$ is large enough to resolve the interactions
at the Helmholtz parameter $k$. 
When $N$ is smaller than that, we observe a worse scaling since the
assumption that far-interactions are low-rank is no longer valid at
the tolerance of FLAM.
We plot the timing results corresponding to three different values of 
$k$ in~\cref{fig:speed}. The times are as recorded for a laptop with
16Gb of RAM and an Intel Core i7-6600U CPU at 2.60GHz with 4 cores.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{fig/speed_res.pdf}
\caption{Time taken $(t)$ in seconds to evaluate the determinant $f_{C}^{N}(k)$ as
a function of $N$ for three different values of $k$.}
\label{fig:speed}
\end{figure}
